Dynamic Transition Analysis with TIMES

### 2020-09-17 doc/2020-03-paper/results.tex
added 5th scenario text
Former-commit-id: b5d9e1780d0f4060074e878d725c382be900daa7
Former-commit-id: 1c02e10ccb10f21f0f0858db27963f6d5f6bf642

Using both emerging technologies with new nuclear reactors (Fig. \ref{scen4}) results in rapid decarbonization. Both 2030 and 2050 emission targets are met, and an additional emissions reduction of 32 Mt occurs by 2100. The deployment of 50 MW nuclear obviates the need to invest in offshore wind, lithium-ion storage, and \gls{CCS}. Hydrogen plays a significant role in decarbonization, but it is deployed slightly later compared with Scenario 3, from 2037 instead. The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies(62\%), onshore wind (20\%), and nuclear (13\%). From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3. The cost of this transition is \textbf{2,804,753 MUSD}.

\begin{figure}[htb] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nonuc}
\caption{Conventional technologies, no new nuclear.}
\label{scen1}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nuc}
\caption{Conventional technologies, with new nuclear.}
\label{scen2}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nonuc}
\caption{Emerging technologies, no new nuclear.}
\label{scen3}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nuc}
\caption{Emerging technologies, no new nuclear.}
\label{scen4}
\end{figure}

>>>>

Deploying both emerging technologies with new nuclear reactors (Fig. \ref{scen4}) results in rapid decarbonization. Both 2030 and 2050 emission targets are met, and an additional emissions reduction of 32 Mt occurs by 2100. The deployment of 50 MW nuclear obviates the need to invest in offshore wind, lithium-ion storage, and \gls{CCS}. Hydrogen plays a significant role in decarbonization, but it is deployed slightly later compared with Scenario 3, from 2037 instead. The amount of electricity diverted to storage technologies is 29,733 TWh, primarily from solar and emerging solar technologies(62\%), onshore wind (20\%), and nuclear (13\%). From this, 24,264 TWh of hydrogen is generated, produced entirely from PEM electrolysis, as there was no urgency to deploy \gls{AEC} as in Scenario 3. The cost of this transition is \textbf{2,804,753 MUSD}.

The fifth scenario's results (Fig. \ref{scen5}) closely resemble those of the third scenario (Fig. \ref{scen3}). However, \gls{SOEC}s rapidly replace a large fraction of aging \gls{PEMEC}s. Some \gls{PEMEC}s remain in the mix until 2100 despite their lower efficiency due to their lower cost. Both 2030 and 2050 emission targets are met, but no additional emission reductions occur beyond 2050. The amount of electricity diverted to storage technologies is 41,752 TWh, primarily from solar and emerging solar technologies(48\%), onshore wind (28\%), and fixed-bottom offshore wind (20\%). From this, 35,550 TWh of hydrogen is generated, mostly from \gls{SOEC} (56\%), \gls{PEMEC} (43\%). \gls{AEC} contributes a mere 0.95\% of the total hydrogen, and \gls{PWS} plays the smallest role at 0.05\%. The cost of this transition is \textbf{3,180,613 MUSD}.

\begin{figure}[htb] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nonuc}
\caption{Scenario 1 - Conventional technologies, no new nuclear.}
\label{scen1}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.42]{figures/conv_nuc}
\caption{Scenario 2 - Conventional technologies, with new nuclear.}
\label{scen2}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nonuc}
\caption{Scenario 3 - Emerging technologies, no new nuclear.}
\label{scen3}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/newtechs_nuc}
\caption{Scenario 4 - Emerging technologies, with new nuclear.}
\label{scen4}
\end{figure}

\begin{figure}[h] 
\centering
\vspace*{-3cm}
\includegraphics[scale=0.41]{figures/lowtrltech_nonuc}
\caption{Scenario 5 - Emerging technologies and nascent hydrogen technologies, no new nuclear.}
\label{scen5}
\end{figure}
